\documentclass{article}

% Include necessary LaTeX packages for math
\usepackage{amsmath} % for advanced math symbols and environments
\usepackage{amsfonts} % for additional math fonts
\usepackage{amssymb} % for additional math symbols
\usepackage{mathtools} % for additional math tools and symbols
\usepackage{bm} % for bold math symbols
\usepackage{mathrsfs} % for additional math fonts

% Set up document formatting (optional)
\usepackage{geometry} % for adjusting page margins and size
\usepackage{setspace} % for adjusting line spacing
\usepackage{enumitem} % for customizing lists







\chapter{Introduction to Abstract Algebra and Set Theory}

\section{Basic Set Operations, Relations, and Functions}

In this section, we will cover the basics of set theory, including set operations, relations, and functions. These concepts are fundamental to understanding abstract algebra.

\subsection{Set Operations}

A \textit{set} is a collection of distinct objects, called \textit{elements} or \textit{members}. We usually denote sets using capital letters, like $A$, $B$, and $C$. If an element $x$ belongs to a set $A$, we write $x \in A$. If $x$ does not belong to $A$, we write $x \notin A$.

There are several basic operations on sets that we will use throughout this course:

\begin{itemize} \item \textbf{Union:} The union of two sets $A$ and $B$, denoted $A \cup B$, is the set containing all elements that are in either $A$ or $B$ or both. In other words, A \cup B\={x:x \in A { or } x \in B}.A \cup B = \{x : x \in A \text{ or } x \in B\}.A \cup B\={x:x \in A \text{ or } x \in B}.

    \item \textbf{Intersection:} The intersection of two sets $A$ and $B$, denoted $A \cap B$, is the set containing all elements that are in both $A$ and $B$. In other words, $A \cap B = \{x:x \in A \text{ and }x \in B\}$.

    \item \textbf{Difference:} The difference of two sets $A$ and $B$, denoted $A \setminus B$, is the set containing all elements that are in $A$ but not in $B$. In other words, $A \setminus B = {x:x \in A \text{ and } x \notin B}$. 

    \item \textbf{Complement:} The complement of a set $A$, denoted $A^c$ or $\overline{A}$, is the set containing all elements that are not in $A$. The complement operation requires a \textit{universal set} $U$ as a reference, which contains all the elements under consideration. In other words, $A^c ={x:x \in U \text{ and } x \notin A}$.

    \item \textbf{Cartesian Product:} The Cartesian product of two sets $A$ and $B$, denoted $A \times B$, is the set of all ordered pairs $(a, b)$, where $a \in A$ and $b \in B$. In other words, $A \times B = \{(a,b):a \in A \text{ and } b \in B\}$. 

\end{itemize}

\subsection{Relations}

A \textit{relation} is a set of ordered pairs of elements. More specifically, a relation $R$ on two sets $A$ and $B$ is a subset of their Cartesian product $A \times B$. We say that $a \in A$ is related to $b \in B$ by the relation $R$ if $(a, b) \in R$. We write this as $aRb$.

Some common types of relations are:

\begin{itemize} 

\item \textbf{Equivalence Relation:} A relation $R$ on a set $A$ is an equivalence relation if it satisfies the following three properties: 

\begin{enumerate} 

    \item \textit{Reflexivity:} For all $a \in A$, $aRa$. In other words, every element is related to itself. 
    
    \item \textit{Symmetry:} For all $a, b \in A$, if $aRb$, then $bRa$. In other words, if $a$ is related to $b$, then $b$ is related to $a$. 
    
    \item \textit{Transitivity:} For all $a, b, c \in A$, if $aRb$ and $bRc$, then $aRc$. In other words, if $a$ is related to $b$ and $b$ is related to $c$, then $a$ is related to $c$. 
\end{enumerate}


\item \textbf{Partial Order:} A relation $R$ on a set $A$ is a partial order if it satisfies the following three properties: 
    \begin{enumerate} 
        
        \item \textit{Reflexivity:} For all $a \in A$, $aRa$. 
        
        \item \textit{Antisymmetry:} For all $a, b \in A$, if $aRb$ and $bRa$, then $a = b$. In other words, if $a$ is related to $b$ and $b$ is related to $a$, then $a$ and $b$ are equal. 
        
        \item \textit{Transitivity:} For all $a, b, c \in A$, if $aRb$ and $bRc$, then $aRc$. 
        \end{enumerate} 

    \end{itemize}

\subsection{Functions}

A \textit{function} is a special kind of relation between two sets $A$ and $B$. A function $f$ from a set $A$ to a set $B$, denoted $f : A \to B$, is a rule that assigns to each element $a \in A$ a unique element $b \in B$. We write $f(a) = b$ to indicate that the function $f$ maps the element $a$ to the element $b$. The set $A$ is called the \textit{domain} of the function, and the set $B$ is called the \textit{codomain}. The \textit{range} of the function is the set of all elements in $B$ that are the images of elements in $A$. In other words, the range of $f$ is the set ${f(a) : a \in A}$.

A function $f : A \to B$ is called an \textit{injection} or \textit{one-to-one} if every element in $A$ is mapped to a distinct element in $B$. In other words, if $f(a_1) = f(a_2)$, then $a_1 = a_2$.

A function $f : A \to B$ is called a \textit{surjection} (or \textit{onto}) if every element in $B$ is the image of at least one element in $A$. In other words, for every $b \in B$, there exists an $a \in A$ such that $f(a) = b$.

A function $f : A \to B$ is called a \textit{bijection} or has a \textit{one-to-one correspondence} if it is both an injection and a surjection. In other words, $f$ is a bijection if every element in $A$ is mapped to a distinct element in $B$, and every element in $B$ is the image of at least one element in $A$. Bijections are important because they establish a strong correspondence between the elements of $A$ and $B$, indicating that the two sets have the same size or cardinality.
% check this definition...

\subsection{Composition of Functions}

Given two functions $f : A \to B$ and $g : B \to C$, we can define a new function called the \textit{composition} of $f$ and $g$, denoted as $g \circ f : A \to C$. The composition of $f$ and $g$ is defined as follows:

\[
(g \circ f)(a) = g(f(a)) \text{ for all } a \in A
\]

In other words, to compute the value of the composition at $a \in A$, we first apply the function $f$ to $a$, then apply the function $g$ to the result.

\subsection{Inverse Functions}

A function $f : A \to B$ has an \textit{inverse} if there exists a function $g : B \to A$ such that both $g \circ f = \text{id}\_A$ and $f \circ g = \text{id}\_B$, where $\text{id}\_A$ and $\text{id}\_B$ are the identity functions on $A$ and $B$, respectively. The identity function on a set $X$, denoted $\text{id}\_X$, is defined as $\text{id}\_X(x) = x$ for all $x \in X$. If such a function $g$ exists, we denote it as $f^{-1}$ and call it the inverse of $f$.
% fix this definition.

It is important to note that not all functions have inverses. For a function to have an inverse, it must be a bijection. In other words, the function must be both an injection and a surjection. If a function is a bijection, its inverse is unique.

This concludes the first section of Chapter 1 on basic set operations, relations, and functions. In the next section, we will explore Cartesian products and equivalence relations, which are essential tools for understanding more advanced concepts in abstract algebra.


\section{Cartesian Products and Equivalence Relations}

\subsection{Cartesian Products}

The Cartesian product of two sets $A$ and $B$, denoted as $A \times B$, is the set of all ordered pairs $(a, b)$, where $a \in A$ and $b \in B$. More formally,
\[
A \times B = \{(a, b) \mid a \in A, b \in B\}.
\]

\begin{example}
Let $A = \{1, 2\}$ and $B = \{a, b\}$. The Cartesian product $A \times B$ is
\[
A \times B = \{(1, a), (1, b), (2, a), (2, b)\}.
\]
\end{example}

The Cartesian product can be generalized to more than two sets. Given $n$ sets, the Cartesian product is the set of all ordered $n$-tuples.

\subsection{Relations}
A relation $R$ on a set $A$ is a subset of $A \times A$. If $(a, b) \in R$, we write $aRb$ or $a \sim b$. A relation can have the following properties:

\begin{itemize}
\item \textbf{Reflexive}: A relation $R$ is reflexive if for all $a \in A$, $aRa$. In other words, $(a, a) \in R$.
\item \textbf{Symmetric}: A relation $R$ is symmetric if for all $a, b \in A$, $aRb$ implies $bRa$. In other words, if $(a, b) \in R$, then $(b, a) \in R$.
\item \textbf{Transitive}: A relation $R$ is transitive if for all $a, b, c \in A$, $aRb$ and $bRc$ imply $aRc$. In other words, if $(a, b) \in R$ and $(b, c) \in R$, then $(a, c) \in R$.
\end{itemize}

\subsection{Equivalence Relations}
An equivalence relation is a relation that is reflexive, symmetric, and transitive. If a relation $\sim$ is an equivalence relation on a set $A$, then we can partition $A$ into disjoint subsets called equivalence classes.

\begin{definition}
Given an equivalence relation $\sim$ on a set $A$, the equivalence class of an element $a \in A$ is the set of all elements in $A$ that are related to $a$. It is denoted by $[a]$:

\[
[a] = \{x \in A \mid x \sim a\}.
\]

\end{definition}

\begin{theorem}
If $\sim$ is an equivalence relation on a set $A$, then the equivalence classes partition $A$ into disjoint subsets.
\end{theorem}

\begin{proof}
Let $A$ be a set with an equivalence relation $\sim$, and let $a, b \in A$. There are two cases to consider for the intersection of the equivalence classes $[a]$ and $[b]$:

\begin{enumerate}
\item If $a \sim b$, then for any $x \in [a]$, we have $x \sim a \sim b$. Since $\sim$ is symmetric, $b \sim a$, and by transitivity, $x \sim b$. Therefore, $x \in [b]$, and $[a] \subseteq [b]$. Similarly, we can show that $[b] \subseteq [a]$, and thus, $[a] = [b]$.

\item If $a \not\sim b$, then $[a] \cap [b] = \emptyset$. Suppose there exists an element $x \in [a] \cap [b]$. Then $x \sim a$ and $x \sim b$. By symmetry, $b \sim x$, and by transitivity, $a \sim b$. This contradicts our assumption that $a \not \sim b$. Therefore, the intersection must be empty.

\end{enumerate}

In both cases, the equivalence classes are either equal or disjoint, which implies that the equivalence classes partition $A$.
\end{proof}

\begin{example}
Let $A = \mathbb{Z}$, and define an equivalence relation $\sim$ on $\mathbb{Z}$ such that $a \sim b$ if and only if $a \equiv b \pmod{3}$. The equivalence classes are:
\begin{align*}
[0] &= \{\dots, -6, -3, 0, 3, 6, \dots\}, \\
[1] &= \{\dots, -5, -2, 1, 4, 7, \dots\}, \\
[2] &= \{\dots, -4, -1, 2, 5, 8, \dots\}.
\end{align*}

These equivalence classes partition $\mathbb{Z}$ into disjoint subsets.
\end{example}



\end{document}